---
title: "HW3"
author: "Liam Gilson"
format: html
editor: visual
---

---

<https://github.com/liamgilson18/ENVS-193DS_homework03_.git>

```{r}
install.packages("here")
```

```{r}
library(tidyverse)   # For data manipulation and visualization
library(here)        # For working with file paths
library(gt)          # For creating tables (you could also use flextable instead)
library(janitor)     # For cleaning data

# Optionally, load other helpful packages
# library(readxl)    # If you're reading Excel files
```

#Problem 1 

a. 
With my data I have been tallying how much money I spend on eating out, and seperating that into what week of the quarter it is, and I would like to show the difference in money I spend eating out for each week. To do this, I would like to do statistical tests on the mean money spent per meal, per week, and try to find a trend on my spending habits as the quarter goes on.

b.  
```{r}

data <- read_csv("Book2.csv")

# Group by week_of_quarter and compute mean price
weekly_avg <- data %>%
  group_by(week_of_quarter) %>%
  summarise(mean_price = mean(price, na.rm = TRUE)) %>%
  arrange(week_of_quarter)

# Plot: Mean price per week of the quarter
ggplot(weekly_avg, aes(x = factor(week_of_quarter), y = mean_price)) +
  geom_col(fill = "dodgerblue") +
  labs(
    title = "Mean Spending on Eating Out per Week",
    x = "Week of Quarter",
    y = "Mean Price ($)"
  ) +
  theme_minimal()
```

c.
The mean amount of spending per meal, per week appears to be on the rise as the weeks get closer to the end of the Quarter

d.
```{r}
weekly_avg %>%
  mutate(mean_price = round(mean_price, 1)) %>%
  gt() %>%
  tab_header(
    title = "Average Spending Per Week of the Quarter"
  ) %>%
  cols_label(
    week_of_quarter = "Week of Quarter",
    mean_price = "Mean Price ($)"
  )
```


#Problem 2

a. Since my data has to do with the money I am spending on food, maybe my visual could have something to do with food. Accoring to my data I eat a lot of Woodstocks and Rusties Pizza, so maybe I could a pie chart, where the circle is a pizza and the percent of the total money. I would have to turn my means into percentages of a total, but other than that I would look great.

b.

c.

d.   My work depicts the differences in average cost of meal that I spend each week, as slices of a pizza, which was inspired by my own spendings, when I noticed that I was spending lots of money on pizza. I created my visualization on Google Draw, and my process consisted of finding a good image, created sperations or slices, and putting some quantitative data to display how much of the pie said slice is.


#Problem 3 

a.
This paper has a T-test that was comparing the average concentration of post storm ambient concentrations with ASBS discharge sites. the discharge sites were the predictor variable and the concentrations were the response variable.

b. 
