---
title: "HW3"
author: "Liam Gilson"
format: html
editor: visual
---

---

<https://github.com/liamgilson18/ENVS-193DS_homework03_.git>

```{r}
install.packages("here")
```

```{r}
library(tidyverse)   # For data manipulation and visualization
library(here)        # For working with file paths
library(gt)          # For creating tables (you could also use flextable instead)
library(janitor)     # For cleaning data

# Optionally, load other helpful packages
# library(readxl)    # If you're reading Excel files
```

#Problem 1 

a. 
With my data I have been tallying how much money I spend on eating out, and seperating that into what week of the quarter it is, and I would like to show the difference in money I spend eating out for each week. To do this, I would like to do statistical tests on the mean money spent per week, and try to find a trend on my spending habits as the quarter goes on.

b.  
```{r}

data <- read_csv("Book2.csv")

# Group by week_of_quarter and compute mean price
weekly_avg <- data %>%
  group_by(week_of_quarter) %>%
  summarise(mean_price = mean(price, na.rm = TRUE)) %>%
  arrange(week_of_quarter)

# Plot: Mean price per week of the quarter
ggplot(weekly_avg, aes(x = factor(week_of_quarter), y = mean_price)) +
  geom_col(fill = "dodgerblue") +
  labs(
    title = "Mean Spending on Eating Out per Week",
    x = "Week of Quarter",
    y = "Mean Price ($)"
  ) +
  theme_minimal()
```

c.
The mean amount of spending per week appears to be on the rise as the weeks get closer to the end of the Quarter